Knowledge Base Enhanced Continous Learning for High Accuracy Event Detection

### 2016-09-05 paper/ieeeFormat.tex
forward to 9.14
change to aaai format

@@

\textit{History state} is the proposed data structure to restore the information about what happened. 
Initially, \textit{history state} extracts category-related history data into a set of tuples, which weighs the importance of given words to the specific category, defined in Definition 1 formally. 
Taking the \textit{military} category in  Figure \ref{fig:NSinitializaton} as an example, the history state of \textit{military} contain the words \textit{army}, \textit{military}, and \textit{shootings} etc.

\textit{Recent state} is the proposed data structure to maintain the information about what's happening.
It extracts category-related words from incoming text stream, for each time window.
Still taking the \textit{military} category in  Figure \ref{fig:NSinitializaton} as an example, based on extracted history states, our proposed probabilistic continuous learning model \textsc{HS-Prior-LDA} can recognize the words \textit{libyan} and \textit{rebel} in the time window 2011-07-28 in the text stream are related to the category \textit{military}. 
Furthermore the time series analysis on the neighboring recent states can recognize the set of events' candidate words, and finally detects the events in the text stream. 
In the example of Figure 1, the words \textit{libyan} and \textit{rebel} are related to the \textit{military} event ``\#libya Libyan rebels chief is killed (2011-07-28)''.

@@

\subsection{History States Initialization}\label{subsec:hs_initialization}
In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
The knowledge base such as Wikipedia has the structure of classes, subclasses, instances, and the edges between them. 
This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia.  
But The RDF and other methods often

\begin{enumerate}[labelindent=\parindent,leftmargin=*]
\item Taxonomy Graph \(G^{(0)}\). The directed edges in \(G^{(0)}\) represent the class-subclass relations in the knowledge base. 
Taking Wikipedia for example (Figure \ref{fig:NSinitializaton}), the node \textit{Main topic classifications}\footnote{\url{https://en.wikipedia.org/wiki/Category:Main_topic_classifications}} has the subclass \textit{Society}, further contains the subclass \textit{Politics}, which is the ancestor of the subclass \textit{Military}.
\item Category-Page Bipartite Graph \(G^{(1)}\). 
\item Page-Content Maps \(G^{(2)}\).
\end{enumerate}

@@

\begin{figure}
    \label{fig:modelDesc}
    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
    \caption{\textsc{NSDetector}'s process flow, taking \textit{public security} related events in cyberspace as an example. \textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
\end{figure}

>>>>

\begin{figure}[h]
    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
    \caption{\textsc{NSDetector}'s process flow, taking \textit{public security} related events in cyberspace as an example. \textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
    \label{fig:modelDesc}
\end{figure}

@@

\textit{History state} is the proposed data structure to restore the information about what happened. 
Initially, \textit{history state} extracts category-related history data into a set of tuples, which weighs the importance of given words to the specific category, defined in Definition 1 formally. 
Taking the \textit{military} category in Figure \ref{fig:modelDesc} as an example, the history state of \textit{military} contain the words \textit{army}, \textit{military}, and \textit{shootings} etc.

\textit{Recent state} is the proposed data structure to maintain the information about what's happening.
It extracts category-related words from incoming text stream, for each time window.
Still taking the \textit{military} category in  Figure \ref{fig:modelDesc} as an example, based on extracted history states, our proposed probabilistic continuous learning model \textsc{HS-Prior-LDA} can recognize the words \textit{libyan} and \textit{rebel} in the time window 2011-07-28 in the text stream are related to the category \textit{military}. 
Furthermore the time series analysis on the neighboring recent states can recognize the set of events' candidate words, and finally detects the events in the text stream. 
In the example of Figure \ref{fig:modelDesc}, the words \textit{libyan} and \textit{rebel} are related to the \textit{military} event ``\#libya Libyan rebels chief is killed (2011-07-28)''.

@@

\subsection{History States Initialization}\label{subsec:hs_initialization}
In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
The knowledge base such as Wikipedia has the structure of classes, subclasses, instances, and the edges between them. 
This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia. 
%但是，往往在图上的计算是非常费时的。
%But The RDF and other methods often

\textbf{Taxonomy Graph \(G^{(0)}\)}. The directed edges in \(G^{(0)}\) represent the class-subclass relations in the knowledge base. 
Taking Wikipedia for example (Figure \ref{fig:NSinitializaton}), the node \textit{Main topic classifications}\footnote{\url{https://en.wikipedia.org/wiki/Category:Main_topic_classifications}} has the subclass \textit{Society}, further contains the subclass \textit{Politics}, which is the ancestor of the subclass \textit{Military}.

\textbf{Category-Page Bipartite Graph \(G^{(1)}\)}.

\textbf{Page-Content Maps \(G^{(2)}\)}.

@@
